\Title

### 2022-09-14 Grimaldi-etal-BiolCybernetics.tex
Update on Overleaf.

>>>>

Let's first define a biologically inspired trajectory
inspired by Gye movements. Indeed,
these allow to dynamically actuate
the axis of vision in the visual field of view.
Ton instance, Saccades au rapid movements of the eyeball
which reposition the center of vision. In humans,
these are Very frequent (on average every 3 seconds
[ ]) They reproduced very rapidly.
C- 80ms) and the peak speed is proportional to the
amplitude of the displacement (up to 6000/1 for
a large saccade of 30" of amplitude). At a more
microscopic scale, the gaze moves with au
incessant drift similar to a Brownian-like
trajectory (Poletti pois).
To keep with the generality of the task,
we defined eye movements using a form of
Random walk (Engbent 20"]. This
consists first dro define a finite set of
possible motion. Bayed on the distribution of
biological motions, we simplified it
by selectingasetmotionsetofaye motions as the
cartesian product of N-V- phi-8 linearly spaced motion directions
and NY-speed - 7 different speeds.
(see inset of fg : motion_task, a)
Note that speeds are sampled on a geometric
scale between Yq and v-speed_base : 4.
second, we define the trajectory as segments
Whose duration are drawn from a Poisson
distribution with an average length of
block-length : 20 msflevyfl.int). Finally, the trajectory
is integrated by assuming ① that speeds are
uniformly and independently sampled from the
et of different motions motionset and ② motion
is uniform during a time segment. resulting
instances are giving qualitatively similar
trajectories as those observed for eye movements
as observed for instance in humans (see
figure fig : motion_task - a) .
